%!TEX root=../../main.tex

Considering the current current features of Invenio and the state of the art, we
have defined the following requirements for adding annotation capabilities to
the platform:
\begin{itemize}
  \item The system should be extensible and allow consolidating the existing
        commenting, reviewing, tagging and grouping of records either by
        superseding the existing feature set or by providing a base framework
        upon which other features can build. Future similar features should be
        considered by means of reducing development time.
  \item The integration of the new system and features should be backward
        compatible and transparent to end-users. Basically, the Invenio
        application should continue to function in the same manner as before
        this project, with identical feature set.
  \item The targeted commenting use-case, presented in Section \ref{sec:motiv}
        should be considered of high-priority, as the described workflow, while
        highly used by the community, is inefficient.
  \item The new system should seamlessly integrate with the access control
        features of Invenio. For example, during the review period, records on
        CDS are restricted to only the participating authors and reviewers.
        Thus, any associated metadata should also obey the access control rules.
  \item Disseminating annotations should be possible in a standardised manner,
        alike the harvesting possibilities employed for records.
\end{itemize}

The first considered option was using one of the systems previously presented,
namely Annotator or Pundit. The first one seems a promising solution, as it
uses a loose data model that can be easily extended to various use cases and
annotation target types. Unfortunately, the software is involved more on the
frontend aspect, with only minimal infrastructure for dissemination and
storage. Also, the project focuses more on annotating fragments of HTML
documents, which does not fit the targeted commenting use case; records in
Invenio provide the full text usually as PDF documents and such, a proper
solution must be implemented in order to allow making references inside them.

The Pundit project is more complete in terms of features, allowing to annotate
various content types out of the box (text, multimedia) and providing a rich
editor which allows embedding RDF graphs and attaching external files. This
option was designed more as a standalone application and not as a lightweight
wrapper like Annotator, providing features such as authentication, or a
complete backend including both storage and dissemination via a REST interface.
This made it unsuitable for a seamless integration with Invenio, which would
have meant stripping any unnecessary components while preserving the required
functionality.

FIXME: notes offline mode

The careful evaluation of the existing alternatives lead us to consider
implementing a custom solution which, on one hand, would satisfy all the user
requirements and also allow for a gradual integration in the existing Invenio
framework. Nevertheless, existing components and ideas would be reused and
standard practices would be strictly followed, especially in terms of metadata
dissemination.

The next subsection will give an abstract overview of the proposed system,
while Section \ref{sec:impl} will detail the delivered feature set and
implementation details. Due to the overlap of this project with a major
refactoring of the Invenio project, certain miscellaneous tasks were carried
out in order to provide a working base for the new features; this is briefly
discussed in Subsection \ref{sec:v2}.
